Neural Models for Target-Based Computer-Assisted Musical Orchestration

### 2020-08-17 paper/aimusic2020/paper.tex
Add aimusic2020 paper

% -----------------------------------------------
% Template for ISMIR Papers
% 2020 version, based on previous ISMIR templates

% Requirements :
% * 6+n page length maximum
% * 4MB maximum file size
% * Copyright note must appear in the bottom left corner of first page
% * Clearer statement about citing own work in anonymized submission
% (see conference website for additional details)
% -----------------------------------------------

\documentclass{article}
\usepackage[T1]{fontenc} % add special characters (e.g., umlaute)
\usepackage[utf8]{inputenc} % set utf-8 as default input encoding
\usepackage{ismir,amsmath,cite,url}
\usepackage{graphicx}
\usepackage{color}

% Optional: To use hyperref, uncomment the following.
\usepackage[bookmarks=false,hidelinks]{hyperref}
% Mind the bookmarks=false option; bookmarks are incompatible with ismir.sty.

\usepackage{lineno}
%\linenumbers
\newcommand{\carmine}[1]{\textbf{\color{red} Carmine => #1}}
\renewcommand{\baselinestretch}{1}

% Title.
% ------
\title{Neural models for target-based computer-assisted musical orchestration: a preliminary study}

% Note: Please do NOT use \thanks or a \footnote in any of the author markup

% Single address
% To use with only one author or several with the same address
% ---------------
%\oneauthor
% {Names should be omitted for double-blind reviewing}
% {Affiliations should be omitted for double-blind reviewing}

% Two addresses
% --------------
%\twoauthors
%  {First author} {School \\ Department}
%  {Second author} {Company \\ Address}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author}

% Three addresses
% --------------
%\threeauthors
%  {First Author} {Affiliation1 \\ {\tt author1@ismir.edu}}
%  {Second Author} {\bf Retain these fake authors in\\\bf submission to preserve the formatting}
%  {Third Author} {Affiliation3 \\ {\tt author3@ismir.edu}}

%% To make customize author list in Creative Common license, uncomment and customize the next line
%  \def\authorname{First Author, Second Author, Third Author}

% Four or more addresses
% OR alternative format for large number of co-authors
% ------------
\multauthor
{First author$^1$ \hspace{1cm} Second author$^1$ \hspace{1cm} Third author$^2$} { \bfseries{Fourth author$^3$ \hspace{1cm} Fifth author$^2$}\\
  $^1$ Department of Computer Science, University , Country\\
$^2$ International Laboratories, City, Country\\
$^3$  Company, Address\\
{\tt\small CorrespondenceAuthor@ismir.edu, PossibleOtherAuthor@ismir.edu}
}
\def\authorname{First author, Second author, Third author, Fourth author, Fifth author}

\sloppy % please retain sloppy command for improved formatting

@@

%
\maketitle
%
\begin{abstract}
In this paper we will do a preliminary exploration on how neural networks can be used for the task of target-based computer-assisted musical orchestration. We will show how it is possible to model this  musical problem as a classification task and we will propose two deep learning models. We will show, first, how they perform as classifiers for musical instrument recognition by comparing them with specific baselines. We will then show how they perform, both qualitatively and quantitatively, in the task of computer-assisted orchestration by comparing them with state-of-the-art systems. Finally, we will highlight benefits and problems of neural approaches for assisted orchestration and we will propose possible future steps.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\begin{figure}
\includegraphics[scale=0.17]{figs/method.png}
\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.22]{figs/CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{center}
\end{figure}

@@

\begin{figure}
\center{
\includegraphics[scale=0.4]{figs/CNN_vs_ResNet.png}}
\caption{Best overall accuracy for CNN with LSTM and ResNet depending on the number of instruments in the combinations used for training. \label{cnn_vs_resnet}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{figs/Acc_vs_N_CNN.png}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM depending on the number of instruments in the combinations. \label{best_acc_cnn}}
\end{center}
\end{figure}

@@

\begin{equation}
M_N(\hat{X})_i = \left\{\begin{array}{ll}
1 \text{ if } i \in I_N(\hat{X})\\
0 \text{ otherwise}
\end{array}\right.
\label{NMax}
\end{equation}
and $I_N(\hat{X})$ is the set of indices containing the $N$ first maximums of the vector $\hat{X}$.

@@

Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ from Eqn. \eqref{eval}. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.40]{figs/Acc_vs_N_ResNet.png}
\caption{Best overall accuracy and for each instrument obtained by the ResNet depending on the number of instruments in the combinations. \label{best_acc_resnet}}
\end{center}
\end{figure}

@@

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}
  \end{center}
  \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \eqref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}
\end{table*}

@@

For quantitative evaluation, we used the distance metric defined in Eqn. \eqref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\hat{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

\begin{equation}\label{distance}
d(x, \tilde{x}) =\lambda_1 \sum_k \delta_{k1}(x_k - \tilde{x}_k) + \lambda_2 \sum_k \delta_{k2}|x_k - \tilde{x	}_k| \\
\end{equation}
where 
$
\delta_{k1} = 
\begin{cases}
1, \text{if   } x_k \ge \tilde{x}_k \\
0, \text{otherwise}
\end{cases} 
$, $
\delta_{k2} = 
\begin{cases}
1, \text{if   } x_k < \tilde{x}_k \\
0, \text{otherwise}
\end{cases}.
$\\

@@

% For bibtex users:
%\bibliography{paper}

\begin{thebibliography}{99}

\bibitem{FerVic2013} Jose David Fern\'andez and Francisco Vico. {AI Methods in Algorithmic Composition: A Comprehensive Survey}. Journal of Artificial Intelligence Research, vol.48, pp. 513--582, 2013.

\bibitem{Ari2005} Christopher Ariza, {Navigating the landscape of computer aided algorithmic composition systems: A definition, seven descriptors, and a lexicon of systems and research}. In Proceedings of the International Computer Music Conference, 2005.

\bibitem{Maresz2003}
Yan Maresz, {On Computer-Assisted Orchestration}. Contemporary Music Review, vol. 32, n. 1, pg. 99-109, Routledge, 2013.

\bibitem{Carpentier2010}
Gr\'egoire Carpentier, Damien Tardieu, Jonathan Harvey, G\'erard Assayag and Emmanuel Saint-James. {Predicting Timbre Features of Instrument Sound Combinations: Application to Automatic Orchestration}, Journal of New Music Research, vol. 39, n. 1, pg. 47-61, Routlegde, 2010.

\bibitem{Benetos07}
Emmanouil Benetos, Margarita Kotti, and Constantine Kotropoulos.
\newblock Large scale musical instrument identification.
\newblock Sound and Music Computing Conference, Greece, 2007.

\bibitem{Bhardwaj17}
Siddharth Bhardwaj.
\newblock Audio data augmentation with respect to musical instrument
  recognition.
\newblock Master's thesis, 2017.

\bibitem{Bian19}
Wenhao Bian, Jie Wang, Bojin Zhuang, Shaojun~Wang Jiankui~Yang, and Jing Xiao.
\newblock Audio-based music classification with densenet and data augmentation.
\newblock arXiv preprint, https://arxiv.org/abs/1906.11620v1, 2019.

\bibitem{Cella2020}
Carmine-Emanuele Cella.
\newblock Orchidea: a comprehensive framework for target-based assisted orchestration.
\newblock In preparation; available on request from the author, 2020.

\bibitem{Cella2020b}
Carmine-Emanuele Cella, Daniele Ghisi, Vincent Lostanlen, Fabi\'en Levy, Yan Maresz and Joshua Fineberg.
\newblock OrchideaSOL: a dataset of extended instrumental techniques for computer-aided orchestration.
\newblock ICMC (under review), 2020.

\bibitem{Chetry05}
Nicolas Chetry, Mike Davies, and Mark Sandler.
\newblock Musical instrument identification using LSF and K-means.
\newblock Audio Engineering Society Convention 118, 2005.

\bibitem{He15}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
\newblock Deep residual learning for image recognition.
\newblock arXiv preprint, https://arxiv.org/abs/1512.03385, 2015.

\bibitem{Hershey17}
Shawn Hershey, Sourish Chaudhuri, Daniel P.~W. Ellis, Jort~F. Gemmeke, Aren
  Jansen, R.~Channing Moore, Manoj Plakal, Devin Platt, Rif~A. Saurous, Bryan
  Seybold, Malcolm Slaney, Ron~J. Weiss, and Kevin Wilson.
\newblock CNN architectures for large-scale audio classification.
\newblock IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2017.

\bibitem{Hochreiter97}
Sepp Hochreiter and J\"{u}rgen Schmidhuber.
\newblock Long short-term memory.
\newblock {\em Neural Comput.}, 9(8):1735–1780, November 1997.

\bibitem{Kitahara05}
Tetsuro Kitahara, Masataka Goto, and Hiroshi~G. Okuno.
\newblock Pitch-dependent identification of musical instrument sounds.
\newblock Applied Intelligence 23, 267–275, Springer, 2005.

\bibitem{lostanlen16}
Vincent Lostanlen and Carmine-Emanuele Cella.
\newblock Deep convolutional networks on the pitch spiral for musical
  instrument recognition. ISMIR, 2016.

\bibitem{mcfee15}
Brian McFee, Colin Raffel, Dawen Liang, Daniel~P.W. Ellis, Matt McVicar, Eric
  Battenberg, and Oriol Nieto.
\newblock librosa: Audio and music signal analysis in python.
\newblock {P}roceedings of the 14th {P}ython in {S}cience {C}onference, 2015.

\bibitem{scikit-learn}
Fabian Pedregosa, Ga\"el Varoquaux, Alexandre
Gramfort, Vincent Michel, Bertrand Thirion, Olivier
Grisel, Mathieu Blondel, Peter Prettenhofer, Ron
Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre
Passos, David Cournapeau, Matthieu Brucher,
Matthieu Perrot, \'Edouard Duchesnay.
\newblock Scikit-learn: Machine learning in {P}ython.
\newblock {\em Journal of Machine Learning Research}, 12:2825--2830, 2011.

\bibitem{Salamon17}
Justin Salamon and Juan~Pablo Bello.
\newblock Deep convolutional neural networks and data augmentation for
  environmental sound classification.
\newblock {\em IEEE Signal Processing Letters}, 24(3):279–283, Mar 2017.

\bibitem{McKinney2003}
Martin F. McKinney and Jeroen Breebaart.
\newblock Features for Audio and Music Classification.
\newblock ISMIR, 2003.

\bibitem{Cella18}
Carmine-Emanuele Cella and Philippe Esling, {Open-source modular toolbox for computer-aided orchestration}, Proc. of the Timbre conference, Montreal, Canada, 2018.

\bibitem{Gillick19}
Jon Gillick, Carmine-Emanuele Cella and David Bamman. {Estimating Unobserved Audio Features for Target-Based Orchestration}, ISMIR, 2019.

\end{thebibliography}

>>>>

%%%%%%%%%%%%%%%%%%%% file CSMC_MUME_LaTeX_Template.tex %%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Journal of Creative Music Systems.
% Copyright: http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{url}
\usepackage{apacite}
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\pagestyle{headings}

@@

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Neural Models for Target-Based Computer-Assisted Musical Orchestration}

% a short form should be given in case it is too long for the running head
\titlerunning{Running Title}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{AuthorA\inst{1}\and AuthorB\inst{2} \thanks{Please place acknowledgement here.}}
%
% if the names of the authors are too long for the running head, please use the format: AuthorA et al.
\authorrunning{AuthorA and AuthorB (or AuthorA et al. if too long)}

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{InstituteA \and InstituteB\\ \email{author@phdsrus.ac.uk}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\maketitle

\begin{abstract}
In this paper we will do a preliminary exploration on how neural networks can be used for the task of target-based computer-assisted musical orchestration. We will show how it is possible to model this  musical problem as a classification task and we will propose two deep learning models. We will show, first, how they perform as classifiers for musical instrument recognition by comparing them with specific baselines. We will then show how they perform, both qualitatively and quantitatively, in the task of computer-assisted orchestration by comparing them with state-of-the-art systems. Finally, we will highlight benefits and problems of neural approaches for assisted orchestration and we will propose possible future steps.
\end{abstract}
%
\section{Introduction}\label{sec:introduction}

@@

\begin{figure}
\includegraphics[scale=0.17]{../latex/figs/method.png}
\caption{An overview of the proposed method for assisted orchestration with neural models. Instruments and pitches are determined as peaks of the output probability distribution, while the dynamics are computed by quantizing the probabilities. \label{fig:method}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.22]{../latex/figs/CNN_LSTM_diagram.png}
\caption{Diagram of the CNN with LSTM architecture. \label{cnn_lstm}}
\end{center}
\end{figure}

@@

\begin{figure}
\center{
\includegraphics[scale=0.4]{../latex/figs/CNN_vs_ResNet.png}}
\caption{Best overall accuracy for CNN with LSTM and ResNet depending on the number of instruments in the combinations used for training. \label{cnn_vs_resnet}}
\end{figure}

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.4]{../latex/figs/Acc_vs_N_CNN.png}
\caption{Best overall accuracy and for each instrument obtained by the CNN with LSTM depending on the number of instruments in the combinations. \label{best_acc_cnn}}
\end{center}
\end{figure}

@@

%\begin{equation}
%M_N(\hat{X})_i = \left\{\begin{array}{ll}
%1 \text{ if } i \in I_N(\hat{X})\\
%0 \text{ otherwise}
%\end{array}\right.
%\label{NMax}
%\end{equation}
and $I_N(\hat{X})$ is the set of indices containing the $N$ first maximums of the vector $\hat{X}$.

@@

%Fig. \ref{best_acc_cnn} and Fig. \ref{best_acc_resnet} show the maximum accuracy computed using the function $f$ from Eqn. \eqref{eval}. For ResNet, the variance in accuracy is much smaller until $N$ reaches 5, at which point it becomes similar to the CNN. The results on both figures show consistency on the relative accuracy of instruments, which was for us the first step towards the validation of this method. Flute, Trombone and Trumpet yield the worst results for both models.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=0.40]{../latex/figs/Acc_vs_N_ResNet.png}
\caption{Best overall accuracy and for each instrument obtained by the ResNet depending on the number of instruments in the combinations. \label{best_acc_resnet}}
\end{center}
\end{figure}

@@

\begin{table*}
  \begin{center}
    \label{orch_eval}
    \begin{tabular}{|c|c|c|c|c|c|c|c|c|c}
     \hline
      \textbf{Model} & \textbf{Ob + Bn} & \textbf{Bn} & \textbf{Bass cl.} & \textbf{Bell 1} & \textbf{Bell 2} & \textbf{Multiph. 1} & \textbf{Car horn} & \textbf{Boat} $\ldots$ \\
      \hline
      CNN with LSTM & 0.17 & 0.28 & 0.70 & 0.55 & 0.26 & \textbf{1.10} & 0.68 & \textbf{1.12} $\ldots$  \\
      \hline
      ResNet & 0.34 & 0.50 & 0.48 & 0.59 & 0.45 & 0.90 & 0.49 & \textbf{1.16} $\ldots$ \\
      \hline
      \hline
      \textbf{$\ldots$} & \textbf{Wind harp} & \textbf{Chord 1} & \textbf{Multiph. 2} & \textbf{Chord 2} & \textbf{Gong} & \textbf{Scream} & \textbf{Brass} & \textbf{Average}  \\
      \hline
      $\ldots$ & 0.55 & 0.79 & 0.70 & 0.57 & 0.73 & \textbf{1.14} & 0.79 & 0.71\\
      \hline
      $\ldots$  & 0.61 & 0.86 & 0.51 & 0.37 & 0.71 & \textbf{1.03} & \textbf{1.05} & 0.66 \\
      \hline
    \end{tabular}
  \end{center}
%  \caption{Quantitative comparison of orchestrations as ratios to Orchidea. Eqn. \eqref{distance} was used with $\lambda_1 = 0.5$ and $\lambda_2 = 10$ to compute distances between orchestrations and targets. What is shown is the ratio between the distance calculated and Orchidea's distance for the same target. A value less than 1 means that the model performed worse (i.e. had a larger distance), and a value greater than 1 means the model performed better than Orchidea. The last column shows the ratio of the average distances for the model across all targets.}
\end{table*}

@@

%For quantitative evaluation, we used the distance metric defined in Eqn. \eqref{distance} to calculate differences in timbre between targets and solutions. This metric is proposed in \cite{Cella2020} as part of the cost function used in Orchidea during the optimization. The equation takes in the full FFT of the target $x$ and full FFT of the solution $\hat{x}$. Then for each bin $k$ of the FFT, it calculates the absolute difference between the values. The differing values of $\lambda_1$ and $\lambda_2$ allow the metric to penalize the solution in different ways.

@@

\begin{equation}\label{distance}
d(x, \tilde{x}) =\lambda_1 \sum_k \delta_{k1}(x_k - \tilde{x}_k) + \lambda_2 \sum_k \delta_{k2}|x_k - \tilde{x	}_k| \\
\end{equation}
where 
%$
%\delta_{k1} = 
%\begin{cases}
%1, \text{if   } x_k \ge \tilde{x}_k \\
%0, \text{otherwise}
%\end{cases} 
%$, $
%\delta_{k2} = 
%\begin{cases}
%1, \text{if   } x_k < \tilde{x}_k \\
%0, \text{otherwise}
%\end{cases}.
%$\\

@@

\bibliographystyle{apacite}
\bibliography{paper}
% For bibtex users:
%\bibliography{paper}
%\bibliographystyle{apalike}
%\begin{thebibliography}{99}
%
%\bibitem{FerVic2013} Jose David Fern\'andez and Francisco Vico. {AI Methods in Algorithmic Composition: A Comprehensive Survey}. Journal of Artificial Intelligence Research, vol.48, pp. 513--582, 2013.
%
%\bibitem{Ari2005} Christopher Ariza, {Navigating the landscape of computer aided algorithmic composition systems: A definition, seven descriptors, and a lexicon of systems and research}. In Proceedings of the International Computer Music Conference, 2005.
%
%\bibitem{Maresz2003}
%Yan Maresz, {On Computer-Assisted Orchestration}. Contemporary Music Review, vol. 32, n. 1, pg. 99-109, Routledge, 2013.
%
%\bibitem{Carpentier2010}
%Gr\'egoire Carpentier, Damien Tardieu, Jonathan Harvey, G\'erard Assayag and Emmanuel Saint-James. {Predicting Timbre Features of Instrument Sound Combinations: Application to Automatic Orchestration}, Journal of New Music Research, vol. 39, n. 1, pg. 47-61, Routlegde, 2010.
%
%
%\bibitem{Benetos07}
%Emmanouil Benetos, Margarita Kotti, and Constantine Kotropoulos.
%\newblock Large scale musical instrument identification.
%\newblock Sound and Music Computing Conference, Greece, 2007.
%
%\bibitem{Bhardwaj17}
%Siddharth Bhardwaj.
%\newblock Audio data augmentation with respect to musical instrument
%  recognition.
%\newblock Master's thesis, 2017.
%
%\bibitem{Bian19}
%Wenhao Bian, Jie Wang, Bojin Zhuang, Shaojun~Wang Jiankui~Yang, and Jing Xiao.
%\newblock Audio-based music classification with densenet and data augmentation.
%\newblock arXiv preprint, https://arxiv.org/abs/1906.11620v1, 2019.
%
%\bibitem{Cella2020}
%Carmine-Emanuele Cella.
%\newblock Orchidea: a comprehensive framework for target-based assisted orchestration.
%\newblock In preparation; available on request from the author, 2020.
%
%\bibitem{Cella2020b}
%Carmine-Emanuele Cella, Daniele Ghisi, Vincent Lostanlen, Fabi\'en Levy, Yan Maresz and Joshua Fineberg.
%\newblock OrchideaSOL: a dataset of extended instrumental techniques for computer-aided orchestration.
%\newblock ICMC (under review), 2020.
%
%\bibitem{Chetry05}
%Nicolas Chetry, Mike Davies, and Mark Sandler.
%\newblock Musical instrument identification using LSF and K-means.
%\newblock Audio Engineering Society Convention 118, 2005.
%
%\bibitem{He15}
%Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
%\newblock Deep residual learning for image recognition.
%\newblock arXiv preprint, https://arxiv.org/abs/1512.03385, 2015.
%
%\bibitem{Hershey17}
%Shawn Hershey, Sourish Chaudhuri, Daniel P.~W. Ellis, Jort~F. Gemmeke, Aren
%  Jansen, R.~Channing Moore, Manoj Plakal, Devin Platt, Rif~A. Saurous, Bryan
%  Seybold, Malcolm Slaney, Ron~J. Weiss, and Kevin Wilson.
%\newblock CNN architectures for large-scale audio classification.
%\newblock IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), 2017.
%
%\bibitem{Hochreiter97}
%Sepp Hochreiter and J\"{u}rgen Schmidhuber.
%\newblock Long short-term memory.
%\newblock {\em Neural Comput.}, 9(8):1735–1780, November 1997.
%
%\bibitem{Kitahara05}
%Tetsuro Kitahara, Masataka Goto, and Hiroshi~G. Okuno.
%\newblock Pitch-dependent identification of musical instrument sounds.
%\newblock Applied Intelligence 23, 267–275, Springer, 2005.
%
%\bibitem{lostanlen16}
%Vincent Lostanlen and Carmine-Emanuele Cella.
%\newblock Deep convolutional networks on the pitch spiral for musical
%  instrument recognition. ISMIR, 2016.
%
%\bibitem{mcfee15}
%Brian McFee, Colin Raffel, Dawen Liang, Daniel~P.W. Ellis, Matt McVicar, Eric
%  Battenberg, and Oriol Nieto.
%\newblock librosa: Audio and music signal analysis in python.
%\newblock {P}roceedings of the 14th {P}ython in {S}cience {C}onference, 2015.
%
%\bibitem{scikit-learn}
%Fabian Pedregosa, Ga\"el Varoquaux, Alexandre
%Gramfort, Vincent Michel, Bertrand Thirion, Olivier
%Grisel, Mathieu Blondel, Peter Prettenhofer, Ron
%Weiss, Vincent Dubourg, Jake Vanderplas, Alexandre
%Passos, David Cournapeau, Matthieu Brucher,
%Matthieu Perrot, \'Edouard Duchesnay.
%\newblock Scikit-learn: Machine learning in {P}ython.
%\newblock {\em Journal of Machine Learning Research}, 12:2825--2830, 2011.
%
%\bibitem{Salamon17}
%Justin Salamon and Juan~Pablo Bello.
%\newblock Deep convolutional neural networks and data augmentation for
%  environmental sound classification.
%\newblock {\em IEEE Signal Processing Letters}, 24(3):279–283, Mar 2017.
%
%\bibitem{McKinney2003}
%Martin F. McKinney and Jeroen Breebaart.
%\newblock Features for Audio and Music Classification.
%\newblock ISMIR, 2003.
%
%\bibitem{Cella18}
%Carmine-Emanuele Cella and Philippe Esling, {Open-source modular toolbox for computer-aided orchestration}, Proc. of the Timbre conference, Montreal, Canada, 2018.
%
%\bibitem{Gillick19}
%Jon Gillick, Carmine-Emanuele Cella and David Bamman. {Estimating Unobserved Audio Features for Target-Based Orchestration}, ISMIR, 2019.
%
%\end{thebibliography}
